Covid-19 infection and attributable mortality in UK long term care facilities: Data quality and methodology report

### 2020-07-16 manuscript/manuscript.Rmd
version 1.0

---
title: "Covid-19 infection and attributable mortality in residents of UK care homes: Cohort study using electronic records (March-June 2020)"
bibliography: references.bib
csl: sage-vancouver.csl
output:
  html_document:
    df_print: paged
    toc: yes
    code_folding: hide
  word_document:
    toc: yes
    reference_docx: template.docx
link-citations: yes
always_allow_html: yes
---

@@

>>>>

---
title: "Covid-19 infection and attributable mortality in UK long term care facilities: Cohort study using active surveillance and electronic records (March-June 2020)"
bibliography: references.bib
csl: sage-vancouver.csl
output:
  html_document:
    df_print: paged
    toc: yes
    code_folding: hide
  word_document:
    toc: yes
    reference_docx: template.docx
link-citations: yes
always_allow_html: yes
---

@@

## Availability of data and materials

Figure 2 and 3 data are available on request to authors. This work uses data provided by residents and collected by the Four Seasons Health Care Group as part of their care and support. These are available from the Four Seasons Health Care Group but restrictions apply to the availability of these data, which were used under license for the current study, and so are not publicly available. Data are however available from the authors upon reasonable request and with permission of the Four Seasons Health Care Group.

### 2020-07-16 manuscript_appendix/manuscript_appendix.Rmd
version 1.0

---
title: 'Incidence of confirmed COVID-19 cases in care home staff and residents: Data
  quality and methodology report'
bibliography: ../manuscript/references.bib
output:
  html_document:
    code_folding: hide
    df_print: kable
    keep_md: yes
    toc: yes
    toc_depth: 1
  word_document:
    toc: yes
    toc_depth: 1
    reference_docx: ../manuscript/template.docx
always_allow_html: yes
---

>>>>

---
title: "Covid-19 infection and attributable mortality in UK long term care facilities: Data quality and methodology report"
bibliography: ../manuscript/references.bib
output:
  html_document:
    code_folding: hide
    df_print: kable
    keep_md: yes
    toc: yes
    toc_depth: 1
  word_document:
    toc: yes
    toc_depth: 1
    reference_docx: ../manuscript/template.docx
always_allow_html: yes
---
